Kindly Bent to Free Us

### 2020-06-02 kindly/sdtyping/extra.tex

Entailment is denoted by $\entail{C}{D}$,
where $D$ is a consequence of the constraints $C$.
We say that $C$ and $D$ are equivalent, $C \equivC D$,
when $\entail{C}{D}$ and $\entail{D}{C}$.
% The base rules for entailment are given in \cref{rules:entail}.
% The rules for classic Herbrand unification and
% projection operators are omitted for brevity (see
% \citep{DBLP:journals/tapos/OderskySW99} for
% details).
%
Following \hmx, we define a cylindric constraint system as
a system which respects the following properties for any variable $x$:
\begin{align*}
  \entail{C&}{\Cproj{x}{C}}
  &\entail{C}{D} &\implies \entail{\Cproj{x}C}{\Cproj{x}D}\\
  \Cproj{x}{(C\wedge \Cproj{x}D)}&\equivC \Cproj{x}{C} \wedge \Cproj{x}D
  & \Cproj{x}{\Cproj{y}D}&\equivC \Cproj{y}{\Cproj{x}D}
\end{align*}

Furthermore, we define a term rewriting system as a system where, for every
types $\tau$,$\tau'$, there exists an equality predicates $\Ceq{\tau}{\tau'}$
which is symmetric, reflexive, transitive, stable under substitution and such that,
for any predicate $P$:
\begin{align*}
  &\entail{\Ceq{x}{y}\wedge \Cproj{x}C \wedge \Ceq{x}{y}}{C}\\
  &\subst{x}{\tau}{P} \equivC \Cproj{x}P \wedge \Ceq{x}{\tau}
                        \text{ where } x\notin\fv{\tau}
\end{align*}
$\CL$ is defined as the smallest cylindric term constraint system that
satisfies the axiom shown in \cref{rules:entail}.

>>>>

Entailment is denoted by $\entail{C}{D}$,
where $D$ is a consequence of the constraints $C$.
We say that $C$ and $D$ are equivalent, $C \equivC D$,
when $\entail{C}{D}$ and $\entail{D}{C}$.
% The base rules for entailment are given in \cref{rules:entail}.
% The rules for classic Herbrand unification and
% projection operators are omitted for brevity (see
% \citep{DBLP:journals/tapos/OderskySW99} for
% details).
%

We directly reuse the following definitions from \hmx.

\begin{property}[Cylindric constraint system]
  A cylindric constraint system is a constraint system
  such that, for any constraint $C$:
\begin{align*}
  \entail{C&}{\Cproj{x}{C}}
  &\entail{C}{D} &\implies \entail{\Cproj{x}C}{\Cproj{x}D}\\
  \Cproj{x}{(C\wedge \Cproj{x}D)}&\equivC \Cproj{x}{C} \wedge \Cproj{x}D
  & \Cproj{x}{\Cproj{y}D}&\equivC \Cproj{y}{\Cproj{x}D}
\end{align*}
\end{property}

\begin{property}[Term rewriting system]
A term rewriting system is a system where, for every
types $\tau$,$\tau'$, there exists an equality predicates $\Ceq{\tau}{\tau'}$
which is symmetric, reflexive, transitive, stable under substitution and such that,
for any predicate $P$:
\begin{align*}
  &\entail{\Ceq{x}{y}\wedge \Cproj{x}C \wedge \Ceq{x}{y}}{C}\\
  &\subst{x}{\tau}{P} \equivC \Cproj{x}P \wedge \Ceq{x}{\tau}
                        \text{ where } x\notin\fv{\tau}
\end{align*}
\end{property}

\begin{definition}[Constraint system with lattice]
$\CL$ is defined as the smallest cylindric term constraint system that
satisfies the axiom shown in \cref{rules:entail}.
\end{definition}
